---
title: "Weight of Fish"
author: "Jeanette Serrano"
date: "Nov 4, 2020"
output: 
  html_document:
    number_sections: true
    toc: true
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->

## Build the best regression model you can that predicts the weight of perch
## Using only two predictor variables  


# Perch Model 

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

```{r}
# read in the fish data 
fishdata <- read.csv(file="Fish.csv", header=TRUE)
PerchData <- filter(fishdata, Species=="Perch") %>% select(-Species)                
```

Now build our models
```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = PerchData,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```
   
### The best two regressor model for Perch is Height and Width, this is also the best overall model as measured by adjusted R- square. The two regressors are Height and the second is Height and Width. 


#Bream Model 

```{r}
# read in the fish data 
fishdata <- read.csv(file="Fish.csv", header=TRUE)
BreamData <- filter(fishdata, Species=="Bream") %>% select(-Species)                
```



```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = BreamData,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```
<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->
  
### For the bream model the best regressor is Height and then L2-Height.
So the adjusted R-squared is 0.9356 for Length 2-Height. 
  

```{r}
MODL1 <- lm(Weight~Length2+Height,data=BreamData)
summary.lm(MODL1)
```

# Smelt Model 

```{r}
# read in the fish data 
fishdata <- read.csv(file="Fish.csv", header=TRUE)
SmeltData <- filter(fishdata, Species=="Smelt") %>% select(-Species)                
```

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = SmeltData,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```


  
### For the Smelt data the best regressor is the L2 Length2 and then L2-Width. 
The adjusted R-squared is about 0.97 for this regressor of L2-Width. 
  
  


  
# Discussion and Final Conclusion
So for the Perch model the R-square is 0.94 the Bream model the R-square is 0.9356 and the Smelt Model the R- square is 0.97 therefore there is no significant relationship between the Smelt Model that one is significantly different. Now the Perch and Bream model are somewhat similar since the numbers are off by a few numbers so I would say those two are similar. The variables are all different from each other but when put in the linear models they come to be the same in the positions that they are in. 
  

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
